No proof nets for \capsabbrev{mll} with units

### 2014-04-18 main/LICS.tex
minor edits, copyright updated

\let\beforesection=\medskip
\let\aftersection=\noindent
\let\aftersubsection=\noindent

@@

\conferenceinfo{CSL-LICS 2014}{July 14--18, 2014, Vienna, Austria} 
\copyrightyear{2014} 
\copyrightdata{978-1-4503-2886-9}
\doi{nnnnnnn.nnnnnnn}

@@

In this paper we establish that the proof equivalence problem for multiplicative linear logic with units is \capsabbrev{pspace}-complete. It follows that there can be no satisfactory canonical notion of proof net: 
\color{red}
if a notion of proof net existed where both the translation from proofs to nets and equality of proof nets are polynomial-time computable, this would imply that \capsabbrev{p}\,=\,\capsabbrev{pspace}.
\color{black}

@@

We will demonstrate the \capsabbrev{pspace}-hardness of \capsabbrev{mll} proof equivalence by an encoding of \capsabbrev{ncg}-reconfiguration in \capsabbrev{mll} proof nets.

@@

\begin{proposition}
\label{prop:element linkings}
The standard linkings of Definition~\ref{def:standard linkings} are proof nets.
\end{proposition}

>>>>

\let\beforesection=\relax%\medskip
\let\aftersection=\relax%\noindent
\let\aftersubsection=\relax%\noindent

@@

\exclusivelicense
\conferenceinfo{CSL-LICS 2014}{July 14--18, 2014, Vienna, Austria} 
\copyrightyear{2014} 
\copyrightdata{978-1-4503-2886-9}
\doi{2603088.2603126}

% FOR PERSONAL USE, ADD:

%"© [Owner] [Year]. This is the author's version of the work. It is posted here for your personal use. Not for redistribution. The definitive version was published in {Source Publication}, http://dx.doi.org/10.1145/{number}."

@@

In this paper we establish that the proof equivalence problem for multiplicative linear logic with units is \capsabbrev{pspace}-complete. It follows that there can be no satisfactory canonical notion of proof net: 
\color{red}
if a notion of proof net were to exist where both the translation from proofs to nets and equality of proof nets are polynomial-time computable, this would imply that \capsabbrev{p}\,=\,\capsabbrev{pspace}.
\color{black}

@@

\noindent
%
We will demonstrate the \capsabbrev{pspace}-hardness of \capsabbrev{mll} proof equivalence by an encoding of \capsabbrev{ncg}-reconfiguration in \capsabbrev{mll} proof nets.

@@

\begin{proposition}
\label{prop:element linkings}
%The standard linkings of Definition~\ref{def:standard linkings} are proof nets.
Standard linkings are proof nets.
\end{proposition}
